---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Live Training

This is an empty repo for [Jared Lander's](https://www.jaredlander.com) [Live Training](https://www.safaribooksonline.com/live-training/courses/beginning-r-programming/0636920140665/).

# Clone this Repo

If you use git please clone this repo then open it as an [RStudio Project](https://support.rstudio.com/hc/en-us/articles/200526207-Using-Projects).

If you don't use git, then please recreate this folder structure, and download `prep/DownloadData.r`, on your computer and open the `LiveJanuary2018.Rproj` file using RStudio.

# Packages

To get started run the following code to install the latest version of the necessary packages.

```{r install.packages,eval=FALSE}
packages <- c('coefplot', 'data.world', 'DBI', 'ggthemes', 'jsonlite', 
              'rprojroot', 'RSQLite', 'tidyverse', 'UsingR')
install.packages(packages)
```

# Data

Data for the class is kept at [data.world](https://data.world/landeranalytics/training). Either download all the data files individually or source `prep/DownloadData.r`.

```{r source-data-file,eval=FALSE}
source('prep/DownloadData.r')
```
